An accelerated algorithm for finding efficient solutions in multiobjective problems with black-box multiextremal criteria\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2022-07-02 2022/OPTIMA/paper.tex
fix

The Pareto front in one of test problems is shown in Fig.~\ref{fig2a} and Fig.~\ref{fig2b}. Here Fig.~\ref{fig2a} corresponds to the Pareto front computed on the uniform grid with the step 0.05 in the search domain whereas Fig.~\ref{fig2b} shows the Pareto front computed by RALR-DA. The averaged HV indices obtained while solving the two-dimensional bi-criteria problems are presented in \textcolor{red}{ Tab.~\ref{tab4_6} (series 1) where column $N$ is the dimension of the MCO problems, column $k$ corresponds to criteria counts and column ``Pareto'' corresponds to the estimation obtained by the grid method.}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig4_6.pdf} 
\caption{\textcolor{red}{ Relative backlog of the HV index ($HV_{Pareto} / HV_{alg}$). }}\label{fig4_6} 
\end{figure}

\textcolor{red}{Fig.~\ref{fig4_6} shows the ratio of the HV indices of the Pareto set to the HV index of a specific algorithm.}

>>>>

The Pareto front in one of test problems is shown in Fig.~\ref{fig2a} and Fig.~\ref{fig2b}. Here Fig.~\ref{fig2a} corresponds to the Pareto front computed on the uniform grid with the step 0.05 in the search domain whereas Fig.~\ref{fig2b} shows the Pareto front computed by RALR-DA. The averaged HV indices obtained while solving the two-dimensional bi-criteria problems are presented in \textcolor{red}{ Tab.~\ref{tab4_6} (series 1) where column $N$ is the dimension of the MCO problems, column $k$ corresponds to criteria numbers and column ``Pareto'' corresponds to the estimation obtained by the grid method.}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig4_6.pdf} 
\caption{\textcolor{red}{ Relative backlog of the HV index ($HV_{alg} / HV_{Pareto} $). }}\label{fig4_6} 
\end{figure}

\textcolor{red}{Fig.~\ref{fig4_6} shows the ratio of the HV index of a specific algorithm to the HV index of Pareto set.}
